---
title: "Problem Set 4"
author: "Christopher Milne"
date: "2/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(ggplot2)
library(gt)
library(devtools)
#These commands load the necessary packages.
data <- read_csv("ps_4_elections-poll-nc09-3.csv", 
                 col_types = cols(timestamp = col_datetime(format = "")))
#The data frame is loaded in and named, with the timestamp variable interpreted as a datetime so it is easier to work with later.
```
# Question 1
There were 
`r data %>% filter(response == "Dem") %>% summarize(n())
#this code filters to only look for people who favored democrats and then outputs the number of such entries` 
respondents who supported the Democratic candidate.

There were `r data %>% 
  group_by(response) %>% 
  filter(response %in% c("Rep", "Und")) %>% 
#These commands group the polled people by what party they favored and isolates only the people who favored the republican or were undecided.
  summarize(party_count = n()) %>% 
#This counts the number of people that fell in each of these groups.
  summarize(diff = party_count[1]-party_count[2])
#This outputs the difference between the first and second rows of party_count, which means it output the difference between the number of people who favored republicans and the number of undecided people.` 
  more respondents who favored the Republican candidate than who were Undecided.

There are two gender variables (`gender` and `gender_combined`). There are `r data %>% 
  filter(gender != gender_combined) %>% 
  summarize(n())
#This filters for only cases where the two gender variables were unequal and outputs the number of such observations.`
  individuals for whom these variables have different values.

There are `r data %>% 
  filter(race_eth == "White", file_race_black != "White") %>% 
summarize(n())
#This filters for entries where in one category a person is denoted as white and in another category the person is not denoted as white and outputs the number of such cases.` 
respondents listed as “White” under `race_eth` who are not listed as “White” under `file_race_black`.

The first `response` of Dem came `r data %>%
  filter(response %in% c("Dem", "Rep")) %>%
  group_by(response) %>% 
#The above commands isolate the party preference of interests and groups people my their response.
  select(response, timestamp) %>% 
#This selects only the necessary variables.
  summarize(min_time = min(timestamp)) %>% 
#Since timestamp is a datetime, the minimum in each grouped category (response) is found and named.
  summarize(time_diff = round(min_time[2]-min_time[1], digits=0))
#The difference is found between the minimum time of response for a republican (second row) and the minimum time of repsonse for a democrat (first row).` 
  minutes (rounded to the nearest minute) before the first `response` of Rep.



# Question 2
```{r, table, echo = FALSE}
x <-data %>% 
  select(response, race_eth, final_weight) %>% 
#Only the needed variable are considered for simplicity
  filter(race_eth != "[DO NOT READ] Don't know/Refused") %>% 
#This removes the undesired case where race was unknown from the data set
  mutate(race_eth = fct_relevel(race_eth, c("White", "Black", "Hispanic", "Asian", "Other"))) %>%
#The race factor is releveled so the races will appear in the desired order when race_eth is later used as a variable in the table.
  group_by(response, race_eth) %>%
  summarize(total = sum(final_weight))
#The entries were grouped by response and race and another variable was added to account not only for how many people were in each group, but also how these people were weighted in the pollling.

y <-x %>% 
  spread(key = response, value = total, fill = 0) %>% 
#This takes the responses and makes each a column with entries being the weighted total. NA values are made to be zero so math functions can still act on them.
  mutate(all = Dem + Rep + Und + `3`) %>% 
  mutate(DEM = Dem/all) %>% 
  mutate(REP = Rep/all) %>% 
  mutate(UND = Und/all) %>% 
#This turns the entries into proportions by establishing the total population for each row and dividing the number of entries in a particular race-repsonse group by this overall row (race) population. Third party preferences are not made to be an output, but they are accounted for so the proportions are not actificially altered by excluding people with third party preferences.
  select(race_eth, DEM:UND)
#The desired column variables are selected, notably excluding third party as a response variable.

gt(y) %>% 
#This uses the gt package to generate a particular style of table.
  tab_header(
    title = "North Carolina 9th District: Voter Preference by Race") %>% 
  tab_source_note("New York Times Upshot/Siena College 2018 live polls") %>% 
#The table is given a title and the course is added as a caption.
  
  cols_label(
    race_eth = "",
    DEM = "Democrat",
    REP = "Republican",
    UND = "Undecided"
) %>% 
#The columns are renamed to be more clear and the race column is left unlabeled to match the desired table.
  fmt_percent(columns = vars(DEM, REP, UND),
                decimals = 0) %>% 
#The proportions are changed to be percentages and are rounded so they don't have any decimals.
  na_if(0) %>%
  fmt_missing(columns = vars(UND), rows =4)
#Since the zero percent entry actually indicates an entry that is NA because there were no repsonses applying to it, the entry is changed to indicate that there is no data for that cell by first making the 0 an NA and then making NA a missing entry.
  
```

# Question 3
```{r, NC Graph, echo = FALSE}
x <- data %>% 
  select(response, educ, final_weight) %>% 
  filter(educ != "[DO NOT READ] Refused")
x %>% 
  mutate(educ = fct_relevel(educ, c("Grade school", "High school", "Some college or trade school",
                                    "Bachelors' degree", "Graduate or Professional Degree"))) %>% 
  group_by(educ) %>% 
  ggplot(aes(y = final_weight, x = educ))+geom_violin()+
  geom_jitter(alpha = .4, width= .2, size = .95)+coord_flip()+
  labs(title = "More Educated Matter Less in North Carolina 9th",
       subtitle = "Poll gives more weight to people who are less likely to participate in polls",
       y= "Weight Given to Respondent in Calculating Poll Results",
       x = NULL,
       caption = "New York Times Upshot/Siena College 2018 live polls")
```

# Question 4
